|

### 2020-03-02 analysis/paper/manuscript.Rmd
Clarify the intent/audience of the NCAM dashboard

```{r biomass, echo = FALSE, fig.cap = '- Screen shot of the "Survey Indices" page of the RStrap Explorer application. The "Basic Inputs" sidebar is fixed across all pages and allows the user to specify the species, NAFO Divisions, season, and survey years of interest. The "Biomass Index" sub-tab is illustrated here. This sub-tab shows a time-series of biomass data with 95% confidence intervals, with a break in the lines when the survey gear changed from an Engle to Campelen trawl, for both cod (*Gadus morhua*; species code 438) and American Plaice (*Hippoglossoides platessoides*; species code 889). All trend lines can be toggled off using plotly’s dynamic user interface. The user also has the ability to hover over the points to compare estimates and export the figure as a png file.'}
knitr::include_graphics("figures/RStrap_dashboard_biomass.png")
```

@@

In the pursuit of an easier and more efficient way to communicate results from NCAM, an interactive and self-contained "dashboard", called NCAM explorer, was developed for the 2018 assessment of Northern cod [@dwyer2019]. We used R-based packages (Table \@ref(tab:pkg)) to construct a tool for exploring the input and output of NCAM, specifically the flexdashboard package to group interactive plotly-based visuals into a dynamic document. We also used the crosstalk package to link the data displayed across multiple plots. Via R Markdown, the dashboard is rendered into a self-contained html file that is reproducible, interactive, and easy to update following modifications to the model or the addition of new data.

>>>>

```{r biomass, echo = FALSE, fig.cap = '- Screen shot of the "Survey Indices" page of the RStrap Explorer application. The "Basic Inputs" sidebar is fixed across all pages and allows the user to specify the species, NAFO Divisions, season, and survey years of interest. The "Biomass Index" sub-tab is illustrated here. This sub-tab shows a time-series of biomass data with 95% confidence intervals, with a break in the lines when the survey gear changed from an Engle to Campelen trawl, for both cod (*Gadus morhua*; species code 438) and American Plaice (*Hippoglossoides platessoides*; species code 889). All trend lines can be toggled off using plotly’s dynamic user interface.'}
knitr::include_graphics("figures/RStrap_dashboard_biomass.png")
```

@@

In the pursuit of an easier and more efficient way to communicate results from NCAM, an interactive "dashboard", called NCAM explorer, was developed for the 2018 assessment of Northern cod [@dwyer2019]. We used R-based packages (Table \@ref(tab:pkg)) to construct a tool for exploring the input and output of NCAM, specifically the flexdashboard package to group interactive plotly-based visuals into a dynamic document. We also used the crosstalk package to link the data displayed across multiple plots. Via R Markdown, the dashboard is rendered into a self-contained html file that is reproducible, interactive, and easy to update following modifications to the model or the addition of new data. The intent of this tool was not to replace detailed documentation on the model, however, it was built to serve as an interactive alternative to a standard presentation for communicating the latest results to an audience with a working knowledge of the model.
